---
title: "Statistical Concepts"
---

```{r}
random_vars <- readRDS("C:/Users/Anjali/Downloads/Causal_Data_Science_Data (1)/Causal_Data_Science_Data/random_vars.rds")

# 1

# Expected value (mean) for each variable
expected_values <- sapply(random_vars, mean)

# Variance for each variable
variances <- sapply(random_vars, var)

# Standard deviation for each variable
standard_deviations <- sapply(random_vars, sd)

# Display the results
results <- data.frame(
  Variable = names(random_vars),
  Expected_Value = expected_values,
  Variance = variances,
  Standard_Deviation = standard_deviations
)

results
```

2.
Comparing standard deviations is not always appropriate, especially when variables have different measurement units or represent fundamentally different characteristics. Additionally, standard deviations should be interpreted in conjunction with other statistical measures and the specific goals of the analysis.
```{r}
#3

# Covariance between two variables
covariance_value <- cov(random_vars$age, random_vars$income)

# Correlation between two variables
correlation_value <- cor(random_vars$age, random_vars$income)

# Display the results
relationship_results <- data.frame(
  Variable1 = "age",
  Variable2 = "income",
  Covariance = covariance_value,
  Correlation = correlation_value
)

relationship_results

```
4.
The correlation is generally easier to interpret compared to covariance, as it is a standardized measure that ranges from -1 to 1.Here the measure of correlation is 0.5479432, which suggests a moderate positive linear relationship.
A positive correlation implies that as one variable increases, the other tends to increase as well.
The magnitude of 0.5479432 indicates a moderate strength of the relationship.
The closer the correlation coefficient is to 1, the stronger the positive linear relationship.
```{r}
#5

# Compute conditional expected value for age <= 18
conditional_expected_value_age_less_than_18 <- mean(random_vars$income[random_vars$age <= 18])

# Compute conditional expected value for age in [18, 65)
conditional_expected_value_age_18_to_65 <- mean(random_vars$income[random_vars$age >= 18 & random_vars$age < 65])

# Compute conditional expected value for age >= 65
conditional_expected_value_age_greater_than_65 <- mean(random_vars$income[random_vars$age >= 65])

# Display the results
conditional_expected_values <- data.frame(
  Age_Group = c("Age <= 18", "Age ∈ [18, 65)", "Age >= 65"),
  Conditional_Expected_Value = c(
    conditional_expected_value_age_less_than_18,
    conditional_expected_value_age_18_to_65,
    conditional_expected_value_age_greater_than_65
  )
)

conditional_expected_values

```




