---
title: "Regression and Statistical Inference"
---

```{r}
#1
data <- readRDS("C:/Users/Anjali/Downloads/Causal_Data_Science_Data (1)/Causal_Data_Science_Data/car_prices.rds")
# Assuming your data is stored in a variable named 'data'
data_dimensions <- dim(data)

# Printing the number of rows and columns
print(paste("Number of rows:", data_dimensions[1]))
print(paste("Number of columns:", data_dimensions[2]))
```
```{r}
#2
# Use str() to get the structure of the data
str(data)

# Use summary() for a summary of the data
summary(data)

# Use head() to display the first few rows of the data
head(data)

```
```{r}
#3
# Include all potential regressors
lm_all <- lm(price ~ ., data=data)
summary(lm_all)

#Let’s build a second regression model, where we only include variables that were statistically significant in the previous model.

# Include only significant regressors
lm_imp <- lm(price ~ enginetype + cylindernumber + enginesize + stroke + peakrpm, data = data)
summary(lm_imp)
```
```{r}
#4.1
# Assuming 'enginetype' is a categorical variable
str(data$enginetype)

# Unique values it can take on
unique_values <- unique(data$enginetype)
print(unique_values)

```
```{r}
#4.2 & 4.3
# Fit a linear regression model with 'enginetype' as the only predictor
model_enginetype <- lm(price ~ enginetype, data =data)
summary(model_enginetype)
```
When compared to the reference level, the 'enginetypeohc' and 'enginetypeohcv' categories have statistically significant effects on the price. The other categories ('enginetypedohcv,' 'enginetypel,' and 'enginetypeohcf') do not have statistically significant effects based on the p-values.<br>
<br>
enginetypeohc: The estimated decrease in price for cars with 'enginetypeohc' compared to the reference level is $7,025. The p-value (0.00112) is less than 0.05, so the effect is statistically significant at the 0.05 significance level.<br>
<br>
enginetypeohcv: The estimated increase in price for cars with 'enginetypeohcv' compared to the reference level is $6,982. The p-value (0.01414) is less than 0.05, so the effect is statistically significant at the 0.05 significance level.<br>
<br>
Changing the value of 'enginetype' involves comparing the effect of different engine types on the predicted price

```{r}
#5

library(dplyr)

# Add a new variable 'seat_heating' with value TRUE for all observations
new_df <- data %>% mutate(seat_heating = TRUE)

# Run a regression with the new variable
model_with_seat_heating <- lm(price ~ . + seat_heating, data = new_df)

# Print the summary of the linear regression model
summary(model_with_seat_heating)
```
Perfect Collinearity: If the new variable has the same value for all observations (in this case, TRUE for all), it will lead to perfect collinearity. Perfect collinearity occurs when one variable can be exactly predicted from another variable or a combination of other variables in the model. In such cases, the regression model cannot estimate the coefficients separately, resulting in NA coefficients.<br>
<br>
Perfect Prediction: If the new variable is perfectly predictive of the dependent variable, the regression model may not be able to estimate the coefficients due to perfect prediction. This can occur when there is no variability in the dependent variable within each level of the new variable.





