---
title: "Directed Acyclic Graphs"
---
```{r}
#1
# Load packages
library(dagitty)
library(ggdag)

# create DAG from dagitty
dag_model <- 'dag {
bb="0,0,1,1"
D [exposure,pos="0.075,0.4"]
Y [outcome,pos="0.4,0.4"]
L [pos="0.2,0.2"]
S [pos="0.3,0.5"]
D -> Y
D -> L
S -> D
S -> Y
L -> S
}
'

# draw DAG
ggdag(dag_model) +
  theme_dag() + # custom theme, can be left out
  geom_dag_edges(edge_color = "black")

```
D represents the treatment variable (having parking spots),<br>
Y represents the outcome variable (sales),<br>
L represents the location, and<br>
S represents the store.<br>
```{r}
data <- readRDS("C:/Users/Anjali/Downloads/Causal_Data_Science_Data (1)/Causal_Data_Science_Data/customer_sat.rds")

#2.1
#
model1 <- lm(satisfaction ~ follow_ups, data = data)
summary(model1)

```
```{r}
#2.2
# Assuming 'subscription' is another column in your dataset
model2 <- lm(satisfaction ~ follow_ups + subscription, data = data)
summary(model2)
```
3.
**Model 1**:<br>
**Coefficients**:<br>
Intercept: 78.8860<br>
Follow-ups: -3.3093<br>
**Interpretation**:<br>
The intercept (78.8860) represents the estimated satisfaction when the number of follow-up calls is zero.<br>
The coefficient for follow-ups (-3.3093) suggests that, on average, for each additional follow-up call, satisfaction decreases by approximately 3.31 units.<br>
**Statistical Significance**:<br>
Both intercept and follow-ups have p-values less than 0.05, indicating statistical significance.<br>
**Model Fit**:<br>
R²=0.658: Approximately 65.8% of the variability in satisfaction is explained by the number of follow-up calls.<br>
<br>
**Model 2**:<br>
**Coefficients**:<br>
Intercept: 26.7667<br>
Follow-ups: 2.1944<br>
Subscription Premium: 44.7222<br>
Subscription Premium+: 18.0722<br>
**Interpretation**:<br>
The intercept (26.7667) represents the estimated satisfaction when follow-up calls and all subscription variables are zero.<br>
The coefficient for follow-ups (2.1944) suggests that, on average, for each additional follow-up call, satisfaction increases by approximately 2.19 units.<br>
The coefficients for subscription levels indicate the change in satisfaction compared to the baseline (assumed to be subscription Starter).<br>
**Statistical Significance**:<br>
All coefficients have p-values less than 0.05, indicating statistical significance.<br>
**Model Fit**:<br>
R² = 0.9597 : Approximately 95.97% of the variability in satisfaction is explained by follow-up calls and subscription levels.<br>
<br>
Model 2 provides a more comprehensive understanding of the factors influencing satisfaction as it includes both follow-up calls and subscription levels.<br>
In Model 2, the positive coefficient for follow-ups suggests that more follow-up calls are associated with higher satisfaction.<br>
The subscription coefficients in Model 2 indicate that, compared to the baseline (Starter), both Premium and Premium+ subscriptions are associated with higher satisfaction.<br>
Overall, Model 2 suggests that, when accounting for subscription levels, both follow-up calls and subscription levels significantly contribute to explaining satisfaction. The high R² value in Model 2 indicates that the combination of follow-up calls and subscription levels explains a large portion of the variability in satisfaction

```{r}
#4
# Assuming 'follow_ups', 'satisfaction', and 'subscription' are column names in dataset
library(dagitty)
library(ggdag)

# Create a DAG model manually
dag_model <- dagitty('dag {
  follow_ups [exposure,pos="1,1"]
  satisfaction [outcome,pos="2,1"]
  subscription [pos="3,1"]

  subscription -> satisfaction
  follow_ups -> satisfaction
}')

# plot adjustment sets
ggdag_adjustment_set(dag_model, shadow = T) +
  theme_minimal() + # custom theme, can be left out
  geom_dag_edges(edge_color = "white")
```

