---
title: "Difference-in-Differences"
---

```{r}
#1
data <- readRDS("C:/Users/Anjali/Downloads/Causal_Data_Science_Data (1)/Causal_Data_Science_Data/hospdd.rds")
# Load necessary libraries
library(dplyr)

# Assuming 'data' is your data frame
# Filter the data for all hospitals before and after treatment
all_before <- data %>% filter(month == "Before") 
all_after <- data %>% filter(month == "After")

# Filter the data for treated hospitals before and after treatment
treated_before <- all_before %>% filter(procedure == 1) 
treated_after <- all_after %>% filter(procedure == 1)

# Filter the data for control hospitals before and after treatment
control_before <- all_before %>% filter(procedure == 0) 
control_after <- all_after %>% filter(procedure == 0)

# Print the results
# Compute the mean satisfaction for each group and time period
mean_satisfaction_treated_before <- mean(treated_before$satis, na.rm = TRUE)
mean_satisfaction_treated_after <- mean(treated_after$satis, na.rm = TRUE)

mean_satisfaction_control_before <- mean(control_before$satis, na.rm = TRUE)
mean_satisfaction_control_after <- mean(control_after$satis, na.rm = TRUE)

# Print the results
cat("Mean satisfaction for treated hospitals before treatment:", mean_satisfaction_treated_before, "\n")
cat("Mean satisfaction for treated hospitals after treatment:", mean_satisfaction_treated_after, "\n")

cat("Mean satisfaction for control hospitals before treatment:", mean_satisfaction_control_before, "\n")
cat("Mean satisfaction for control hospitals after treatment:", mean_satisfaction_control_after, "\n")


```
```{r}
#2
#Option 1: Month + Hospital
model1 <- lm(satis ~ procedure + month + hospital, data = data)
summary(model1)

# Option 2: as.factor(Month) + as.factor(Hospital)
model2 <- lm(satis ~ procedure + as.factor(month) + as.factor(hospital), data = data)
summary(model2)

```
In the analysis,considered two different specifications for the regression model, each incorporating group and time fixed effects. The first specification (Model 1) used numeric representations for months and hospitals (month + hospital), treating them as continuous variables. The second specification (Model 2) utilized categorical representations for months and hospitals (as.factor(month) + as.factor(hospital)), allowing for separate intercepts for each month and hospital category.<br>
**Comparison:**<br>
Model 2 has a higher R-squared value, suggesting that it explains a larger proportion of the variance in satisfaction compared to Model 1.<br>
Model 2 includes fixed effects for individual months and hospitals, providing more detailed insights into the impact of each specific month and hospital on satisfaction



